---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# `mathfunctions`

This is an R package that gives some functions for performing mathematical operations

## Installation

You can install mathfunctions from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("abishekarun/mathfunctions")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
# Get 8th fibonacci number of series 0,1,1,2,3...
mathfunctions::nthFibonacci(8) 
```

## For Developers

Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, and `reciprocal`. 

Similarly, use the internal `log` function as the machinery for the front-end functions such as `naturalLog`, `commonLog`, and `binaryLog`. 

Other functions available are `check.integer`,`nthFibonacci`,`nthRoot` etc.


