---
title: "Using the `mathfunctions` package"
author: "Arun Rajendran"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `mathfunctions` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Note__: This package isn't actually meant to be "serious". I made it just for assignment purposes.

Want to perform some mathematical operations without looking for appropriate operators or searching for relevant functions from different packages. Use this package as one stop for the common mathematical functions. 

```{r}
library(mathfunctions)
```

Want squares, cubes, or reciprocals? Easy.

```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

`apply`-family friendly, too!

```{r}
my_list <- list(1:10, 0.5, -0.7)
## So base-R-boring!
lapply(my_list, function(x) x^2)
## Use powers instead!
lapply(my_list, square)
```

It even comes with the ability to display its output in plot form!

```{r}
reciprocal(1:10, plot_it=TRUE)
```

We can also find nth root of real positive values and negative values(provided the order to take root is odd) and plot the output as well
```{r}
nthroot(1:10,2,plot_it=TRUE)
```

We can also find log of real positive values to base 2,10 or natural log (base e).
```{r}
naturalLog(20)
binaryLog(1024)
commonLog(100)
```

We can find the nth fibonacci number of series by mentioning the first term and second term.
```{r}
#a - First term and b - Second term
nthFibonacci(15) #default a=0 and b=1
nthFibonacci(10,2,3) #Here a=2 and b=3
```

We can find the n factorial of a number.
```{r}
fact_func(4)
```

We can also compute the sum of a finite Arithmetic progression series given the first term,difference and the number of terms in the series.
```{r}
sum_series(5,7,10)
```


We can also check if a given number is integer or not. 
```{r}
check.integer(1.234)
check.integer(12)
#check.integer(TRUE) #Produces a error
```


